### 2022-01-12 src-latex/parts/20-related-work.tex
One sentence per line

\cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images. This work proposes to train an OCR system based on a CNN-
LSTM network with synthetic data and then to fine-tune the model with some pages of real historical annotated text. The results show that this approach gives state-of-the-art results.

@@

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths. For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}. The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value. \cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF. They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version. Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure. Overall, NER F-score drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

>>>>

\cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images.
This work proposes to train an OCR system based on a CNN-LSTM network with synthetic data and then to fine-tune the model with some pages of real historical annotated text.
The results show that this approach gives state-of-the-art results.

@@

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.
\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground truths.
For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}.
The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version.
Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure.
Overall, NER F-score drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.
